%-------------------------
% Resume in Latex
% Author : Austin Jackson
% Based on work by : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{color,soul}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom, custom commands
\setulcolor{blue}

\newcommand{\myLink}[1]{
\ul{\small{\normalfont{\textcolor{blue}{\href{#1}{#1}}}}}
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{2pt} % used to be -5pt
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Austin Jackson} & Email : austinjckson@gmail.com\\
  \myLink{https://www.linkedin.com/in/austindjackson} & Mobile : +1-281-851-9106 \\
\end{tabular*}

%-----------OBJECTIVE-----------------
\section{Objective}
  \small{Software Engineering Intern. Computer Science student with a focus on front-end and back-end development for web and software. Interested in innovative methods of utilizing data and technology to serve the needs of people. Seeking opportunities to learn, collaborate, and create solutions.}
  

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{Houston, TX}
      {Bachelor of Science in Computer Science}{Aug. 2019 -- Dec. 2021}
     \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Science in progress, Electronic Systems Engineering Technology}{Aug. 2017 -- Aug. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University College of Engineering}{College Station, TX}
      {\myLink{https://engineering.tamu.edu/nuclear/profiles/staff.html}}{Jan 2018 to Aug 2019}
      \par{\textit{\small{Information Technology Student Technician}}: Responsible for software solutions, hardware repair for Nuclear Engineering Department. Implemented use of Chocolatey to automate custom software package deployment. Implemented PXE workflow to deploy complex Windows images to the College of Engineering. Answering Help Desk phone calls and email correspondence.}	

    \resumeSubheading
      {SalesNexus}{Houston, TX}
      {\myLink{https://www.salesnexus.com/}}{Jan 2016 - May 2016}
    	  \par{\textit{\small{Software Development Intern}}: Thoroughly testing CRM and marketing automation web platform features and writing automated unit tests. Developed unit tests implementing Selenium for browser automation.}

    \resumeSubheading
      {Keypad}{International}
      {\myLink{http://www.getkeypad.co/}}{Nov 2014 - Nov 2015}
      \par{\textit{Web Developer}: Designed and developed static front-end to showcase the launch of macOS desktop app. Rated Best Communication App of 2014 by iMore.com.}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CougarGrades.io}
      {Open source React app for analyzing grade distribution data for University of Houston courses. Paired with a Python scripts to restructure FOIA acquired CSV data into Firebase-ready NoSQL. Over 2800 unique visitors since September 2019 launch (as of Jan. 2020). Available at \myLink{https://cougargrades.io/}}
    \resumeSubItem{Roboruri}
      {Open source Telegram chatbot for searching, indexing, and referencing anime across multiple websites. Over 200 active users at peak. Available at \myLink{https://github.com/au5ton/Roboruri}}
    \resumeSubItem{LipsumLogin}
      {TAMUhack (2019) hackathon project for secure, passwordless logins using Ethereum/web3 cryptographic signatures. Available at \myLink{https://github.com/au5ton/tamuhack2019}}
    \resumeSubItem{Stego}
      {CodeRED Liftoff (2015) hackathon project for proof-of-concept steganography with PNG images. Available at \myLink{https://git.io/vRX9M}}
    \resumeSubItem{Watchdox}
      {Reverse engineering digital rights management (DRM) used by Blackberry Workspaces to export secure documents. Available at \myLink{https://github.com/au5ton/watchdox}}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Javascript, Python, C++, Java, Bash, MATLAB}
    \resumeSubItem{Technologies}{Node.js, React, Docker, SQL, Firebase, GCE, Git/Github, Maven, Sass, Web3, Arduino}
    \resumeSubItem{Interests}{Open source technologies, Education, Information Security, Cryptocurrencies, Civil rights}
  \resumeSubHeadingListEnd

%--------Extracurricular??-----------
\section{Extracurricular}
  \resumeSubHeadingListStart
  	\item{Teachers Assistant and Volunteer Tutor for High School Computer Science courses from Fall 2014 to Spring 2017.}\vspace{-4pt}
  	\item{Annual Texas Computer Science UIL regional competitor.}\vspace{-4pt}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
